A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Future work and recommendation
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1004 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

In many cases, setting a reasonable cache headers is straightforward,
and should be done by data owners. Framework authors should make it
easy to set the expected lifetime.

>>>>

Even though it is clear that other parts of the Web benefit greatly
from caching, and that the potential for HTTP metadata to better
reflect actual update practices in the Semantic Web is great,
estimating the actual impact of doing so should be done.

@@

In many cases, setting a reasonable cache headers is straightforward,
and should be done by data owners. Framework authors should make it
easy to set the expected lifetime, heeding the metadata association
good practice recommendation of \cite{Jacobs:04:AWW}. If the author is
unable to influence HTTP headers, they should set a
\rdfterm{dct:valid} time into the future and make use of
\rdfterm{dct:modified}.
